Measuring neutron star tidal deformability with Advanced LIGO: a Bayesian analysis of mixed binary observations

### 2016-06-08 Paper/paper.tex
adding stat err 1-d, 2-d figures
updated first two plots

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{How is PE affected if we ignore NS matter effects?}\label{s1:PEwithnoNS}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

the effect of the tidal deformation of the neutron star due to its companion hole
on the emitted GWs. In this section we present the first fully Bayesian Monte-Carlo
study of the effects of this assumption on the recovery of other physical parameters
of NS-BH sources.

>>>>

\section{How is PE affected if we ignore NS matter effects?}\label{s1:PEwithnoNS}
\includegraphics[width=1.8\columnwidth]{plots/SingleSystemEta_q4_0_mc2_25_chi0_50}
\caption{We show here the measured probability distribution for the
dimensionless mass ratio $\eta$ of a binary with
$q = \mbh/\mns = 5.4M_\odot/1.35M_\odot = 4$, $\chibh=+0.5$, and
$\lambdans=2000$. The templates used here {\it ignore} tidal effects.
These figures show that this approximation holds up to (SNR)
$\rho\simeq 30-50$.
In each panel- the dashed red line marks the {\it measured} value of $\eta$,
which is given by the median of its probability distribution.
The {\it true} value is marked by the dashed green line. The difference
between the true and measured values is the systematic bias introduced
by ignoring tidal effects in templates. The darker shading shows
the recovered $90\%$ confidence interval for $\eta$. The width of this
region is a direct measure of our statistical uncertainty.
Comparing systematic and statistical errors, we find that:
at $\rho=20$, $\eta$ measurement is dominated by statistical
errors; at $\rho=30$, the two become comparable; and 
for louder signals ($\rho\simeq50$), the systematic errors dominate.
\label{fig:SingleSystemEtaPDFvsSNR}
\includegraphics[width=1.9\columnwidth]{plots/TNEtaCIWidths90_0_Lambda_SNR}
\caption{
We show here the statistical uncertainty of our measurement of the 
dimensionless mass ratio $\eta$ (at $90\%$ confidence), over the NSBH
parameter space.
Individual panels show the same as a function of BH mass and spin.
Across each row, we see the effect of increasing signal strength (i.e.
SNR) with the NS's tidal deformability $\lambdans$ fixed. Down each
column, we see the effect of increasing $\lambdans$, at fixed SNR.
\label{fig:SingleSystemEtaPDFvsSNR}

@@

NS tidal effects on the emitted GWs. In this section we present a fully
Bayesian analysis of the effects of this assumption on the recovery of NSBH
masses and spins from their GW signals.
